BEE Paper

### 2024-04-14 paper.qmd
add experiment instructions and source code

@@

>>>>

The full experiment instructions can be found as screenshots at [https://github.com/kopy-kat/virtual-currencies-paper/tree/main/experiment_instructions](https://github.com/kopy-kat/virtual-currencies-paper/tree/main/experiment_instructions).

@@

The full source code of the paper and the data analysis can be found at [https://github.com/kopy-kat/virtual-currencies-paper](https://github.com/kopy-kat/virtual-currencies-paper).
